Wikipedia Text Mining and Entropy Analysis

### 2018-12-06 wiki_entropy/wiki_entropy.Rmd
ldp ses analysis code
relative slope analysis

@@

estimate_slope_normal <- function(df, first_pos, second_pos) {

>>>>

normal estimation
```{r}
estimate_slope_normal <- function(df, first_pos, second_pos) {

relative estimation
```{r}

df <- read_csv("wiki_df.csv")

df_tokens <- extract_wiki_tokens(6, 50, df)

NUM_SECTIONS = 5

get_quantiles <- function(df, num_sections) {
  quantile(df$word_order, probs = seq(0, 1, 1/num_sections)) %>% 
    round() %>%
    as_data_frame() %>%
    rename(word_order = value)
}

pos_list <- df_tokens %>%
  group_by(length) %>%
  distinct(word_order) %>%
  split(.$length) %>%
  map(~get_quantiles(.x, NUM_SECTIONS)) %>%
  bind_rows(.id = "length") %>%
  mutate(length = as.numeric(length))

relative_slopes <- function(df, pos_list) {

  get_slope <- function(x) {

    selected_pos <- pos_list %>%
      group_by(length) %>%
      slice(x:(x+1)) %>%
      group_by(length) %>%
      summarise(min = min(word_order),
                max = max(word_order)) %>%
      split(.$length) %>%
      map(~seq(.x$min, .x$max, 1) %>% as_data_frame) %>%
      bind_rows(.id = "length") %>%
      rename(word_order = value) %>%
      mutate(length = as.numeric(length))

    df %>%
      inner_join(selected_pos, by = c("length", "word_order")) %>% 
      group_by(length, word_order) %>%
      summarise(entropy = entropy(n, unit = "log2")) %>%
      lm(entropy ~ length + I(length^2) ++ word_order, data  = .) %>%
      tidy() %>%
      filter(term == "word_order")
  }

  divides <- pos_list %>%
    group_by(length) %>%
    summarise(n = n()) %>%
    summarise(n = mean(n)) %>%
    pull()

  map(1:((divides)-1), get_slope) %>%
    bind_rows(.id = "cut")

relative_slopes(df_tokens, pos_list)

@@
